Case study validations of automatic bullet matching\tnoteref{t1}\tnoteref{t2}

### 2019-11-10 index.Rnw
Fix resolution emphasis thing

The algorithm in \citet{aoas2} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44. This mis-labeling has been corrected now. The scans used to train the model were taken at 20 fold magnification for a resolution of 1.5625 microns per pixel. While magnification is generally of interest in microscopy, **resolution** -- usually measured in microns per pixel -- is of more interest for 3D topographic measurements, as it determines the operative level of available data.

>>>>

The algorithm in \citet{aoas2} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44. This mis-labeling has been corrected now. The scans used to train the model were taken at 20 fold magnification for a resolution of 1.5625 microns per pixel. While magnification is generally of interest in microscopy, \emph{resolution} -- usually measured in microns per pixel -- is of more interest for 3D topographic measurements, as it determines the operative level of available data.
